Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-05 WRITEUP/ms.tex
moved around text in 5.2 and 5.1

Maps of the gas Toomre $Q$ parameter and the effective two-component $Q_{\rm eff}$ parameter along different projection angles during the accretion phase of \flower are shown in \Fig{Q} and \Fig{Q_eff}, respectively (see \Fig{h2density} for examples of clumps identified 
in this snapshot). Fragmentation are expected in regions of low-$Q$. 
Further interpretation and implication of this is discussed in \Sec{origin}.

@@

\subsection{Placing Results in the Context of Existing Observations} \label{sec:diss1}
The population of sub-MCs has dynamics largely
similar to those observed
in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in
terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see
e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity
dispersions of $\sigma\simeq$\,20$-$80\,\kms.
% velocity dispersion, larsons
Their velocity dispersions are also comparable to those observed in the inner Milky way and
nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies
along the locus of $\sigma\propto R^{0.56}$.
Such high velocity dispersions and surface densities are expected since
they are located in the nuclear regions of the
galaxy, where the potential well is also deeper. The higher velocity dispersions (see also 
footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp})
of these MCs can also be understood as they have experienced more recent episodes
of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
In fact, by $z\simeq$\,7.2 (i.e., the snapshot corresponding to an early phase of accretion as
shown in \Fig{SFH}a), \flower has assembled
a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).

% alpha parameters
As shown in \Fig{alpha16}, the virial parameter of the sub-MCs is about $\alpha_{\rm vir}\gtrsim10$, which 
is considerably lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
For the MCs in the satellite galaxies, a lower virial parameter is found 
compared to the (sub-)MCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
% pext
As shown in \Fig{alpha27}, MCs in the main disk of \flower have higher pressure than the sub-MCs.
The lower $\alpha_{\rm vir}$ and $P_{\rm ext}$ of the sub-MCs
compared to their parent MCs are consistent with
the notion that collapsing structures result from local gravitational
instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a},
which are supported by turbulence and rotation on large scales.
%Based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower,
%the MC itself is gravitationally unbound and supported by turbulence (from the feedback of multiple episodes of \SF)
%and galactic rotation on large scales. 
%% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.
%Observationally, virial parameters of clouds form in the galactic disk
%are found to have $\alpha_{\rm vir}$\eq0.2$-$10 \citep{Dobbs08a, Tasker09a}.

For MCs in the satellite galaxies, we find low virial parameters and pressures, suggesting 
that these structures are likely collapsing structures. 
Their virial parameters are comparable with those found in clouds that are formed in the galactic disks 
($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
Thus, this would suggest 
\SF continues as gas from the satellite galaxies is being accreted onto the main galaxies during the EoR.

@@

% different evolutionary stages
In the scaling relations examined, we find similar MC properties 
in relation to those observed in the nearby Universe between the accretion phase and the starburst phase of
\flower (see \Fig{larsons_single}, \Fig{alpha16}, and \Fig{alpha27}).
That is, we do not find any quantitative major differences in the MC properties between the accretion and the starburst phase, which
are separated by $\seq$300\,Myr.

@@

The largest molecular structure identified is essentially the main disk of \flower and breaks down into smaller
substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{larsons16-28}). In any case,
the MCs we identified are much bigger in size and mass than nearby GMCs, which is consistent with
those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.

The high pressure observed in \flower is comparable to what has been observed in local ULIRGs; however, the
molecular clouds in the latter are concentrated within their 
central regions and have typical sizes of $\sim$70$-$100\,pc and masses on the order of $\sim$10$^9$\,\Msun
\citep{Downes98a, Sakamoto08a}. In our simulation, the high pressure MCs of \flower are
found throughout the disk. This difference likely stems from the different physical mechanisms giving rise
to the formation (and thus the nature) of these molecular structures.
For instance, in local ULIRGs, they are probably form by shock compression or cloud-cloud
collision after the large amount of gas from the progenitor galaxy merger
is being funneled toward the central region \citep{Tan00a, Wu18a},  % Tasker09a
whereas in \flower, which is actively accreting gaseous materials
from the surrounding, they are probably form from constant cold gas accretion onto the entire galaxy (without
requiring gas to be funneled into the central region).
This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed
in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}).
The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render
the MCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which would be consistent with/explain the
high $\alpha_{\rm vir}$ found for the MCs in the main disk of \flower.

>>>>

Maps of the gas Toomre $Q$ parameter and the effective two-component $Q_{\rm eff}$ parameter along different projection angles during the accretion phase of \flower are shown in \Fig{Q} and \Fig{Q_eff}, respectively (see \Fig{h2density} for examples of clumps identified 
in this snapshot). Fragmentation are expected in regions of low Toomre Q values.
Further interpretation and implication of this is discussed in \Sec{origin}.

@@

\subsection{Placing Results in the Context of Existing Observations} \label{sec:diss1}

The population of sub-MCs has dynamics largely
similar to those observed
in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in
terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see
e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity
dispersions of $\sigma\simeq$\,20$-$80\,\kms.
% velocity dispersion, larsons
Their velocity dispersions are also comparable to those observed in the inner Milky way and
nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies
along the locus of $\sigma\propto R^{0.56}$.
Such high velocity dispersions and surface densities are expected since
they are located in the nuclear regions of the
galaxy, where the potential well is also deeper. The higher velocity dispersions (see also 
footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp})
of these MCs can also be understood as they have experienced more recent episodes
of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
In fact, by $z\simeq$\,7.2 (i.e., the snapshot corresponding to an early phase of accretion as
shown in \Fig{SFH}a), \flower has assembled
a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).

The high pressure observed in \flower is comparable to what has been 
observed in local ultra-luminous IR galaxies (ULIRGs); however, the
molecular clouds in the latter are concentrated within their 
central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun
\citep{Downes98a, Sakamoto08a}. In our simulation, the high pressure MCs of \flower are
found throughout the disk. This difference likely stems from the different physical mechanisms giving rise
to the formation (and thus the nature) of these molecular structures.
For instance, in local ULIRGs, they are likely form by shock compression and cloud-cloud
collision after large amount of gas from the pair of progenitor galaxies
are being funneled toward the central region \citep{Tan00a, Wu18a}.  % Tasker09a
On the other hand, the highly turbulent structures of \flower likely result from 
constant cold gas accretion onto the entire galaxy (without
requiring gas to be funneled into the central region).
This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed
in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed 
size scales could also result from resolution limit where the true physical scales of MCs in
$z$\,\ssim2 galaxies could be smaller in reality.
The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render
the MCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which is 
consistent with the high $\alpha_{\rm vir}$ found for the MCs in the main disk of \flower.

@@

% different evolutionary stages
In the scaling relations examined, we find similar MC properties 
in relation to those observed in the nearby Universe between the accretion phase and the starburst phase of
\flower (see \Fig{larsons_single}, \Fig{alpha16}, and \Fig{alpha27}).
That is, we do not find any quantitative major differences in the MC properties between the accretion and the starburst phase, which
are separated by $\simeq$300\,Myr.

@@

The largest molecular structure identified is essentially the main disk of \flower and breaks down into smaller
substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{larsons16-28}). Overall,
the MCs we identified are much bigger in size and mass than nearby GMCs, 
but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.

Note that ....
